### 2021-10-09 README.Rmd
Paper accepted for publication in Social Science and Medicine
Title updated in README.Rmd

# Changes in accessibility to food banks and food services during COVID-19 and implications for low income populations in Hamilton, Ontario

@@

Paper submitted to *Social Science and Medicine*

>>>>

# Changes in accessibility to emergency and community food services during COVID-19 and implications for low income populations in Hamilton, Ontario

@@

Forthcoming in *Social Science and Medicine*
